Second order bias correction

### 2021-08-13 second_order_correction.rmd
Autocommit

corrected <- taylorapprox(plogis, mean(eta), sd(eta))
out <- c(NULL
	, mean = mean(plogis(eta))
	, uncorrected = plogis(mean(eta))
	, corrected = corrected
)
print(out)
logitnorm::momentsLogitnorm(mu= mean(eta), sigma = sd(eta))
```

>>>>

corrected <- taylorapprox(plogis, mean(eta), sd(eta))
out <- c(NULL
	, mean = mean(plogis(eta))
	, uncorrected = plogis(mean(eta))
	, corrected = corrected
)
print(out)
logitnorm::momentsLogitnorm(mu= mean(eta), sigma = sd(eta))
emdbook::deltamethod(1/(1+exp(-x)), eta)
```
